Suplementary Material 2: Drawing Publication Plots

### 2023-03-31 S1_replicate_stats_and_plots.Rmd
group name adjustments

## Data Import 9 Western European Populations

@@

```{r}
all_tbls$Dataset  <- rep(c("All births", "Without last birth"),2)
all_tbls$Populations  <- rep(c("9 Western European", "Estonia"),each=2)
all_tbls <- as.data.frame(all_tbls)
row.names(all_tbls) <- paste0(all_tbls$Populations, " populations ",
                              tolower(all_tbls$Dataset)) 
knitr::kable(t(all_tbls),
             caption = paste0("Summary data on the Estonian and other ",
                               "European populations for both ",
                              "all births and wihout last birth for same mothers"))
```

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 position = position_nudge(x = -0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 position = position_nudge(x = 0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("(a) All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 fun.data=mean_se,
                 position = position_nudge(x = -0.1)) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 fun.data=mean_se,
                 position = position_nudge(x = 0.1)) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("(b) Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2b <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = "(b) 9 W-European, all births")

fig2a <- draw_fig_4C(fig4C_EE_plot_data) + 
  labs(subtitle = "(a) Estonia, all births")

fig2d <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(d) 9 W-European, without last b.")

fig2c <- draw_fig_4C(fig4C_EE_nl_plot_data,y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(c) Estonia, without last birth")

>>>>

## Data Import 9 Other European Populations

@@

```{r}
#some labels
estLab <- "Estonian"
westLab <- "9 other European"
```

```{r}
all_tbls$Dataset  <- rep(c("All births", "Without last birth"),2)
all_tbls$Populations  <- rep(c(westLab, estLab),each=2)
all_tbls <- as.data.frame(all_tbls)
row.names(all_tbls) <- paste0(all_tbls$Populations, " populations ",
                              tolower(all_tbls$Dataset)) 
knitr::kable(t(all_tbls),
             caption = paste0("Summary data on the Estonian and other ",
                               "European populations for both ",
                              "all births and wihout last birth for same mothers"))
```

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color=estLab),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color=estLab, fill = estLab),
                 alpha=1,
                 position = position_nudge(x = -0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color=estLab, fill = estLab),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color=westLab),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color=westLab, fill=westLab),
                 alpha=1,
                 shape = 1,
                 position = position_nudge(x = 0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill=westLab),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("(a) All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color=estLab),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color=estLab, fill = estLab),
                 alpha=1,
                 fun.data=mean_se,
                 position = position_nudge(x = -0.1)) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color=estLab, fill = estLab),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color=westLab),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color=westLab, fill=westLab),
                 alpha=1,
                 shape = 1,
                 fun.data=mean_se,
                 position = position_nudge(x = 0.1)) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill=westLab),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("(b) Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2b <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = paste0("(b) ",westLab,", all births"))

fig2a <- draw_fig_4C(fig4C_EE_plot_data) + 
  labs(subtitle = paste0("(a) ",estLab,", all births"))

fig2d <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) +
  labs(subtitle = paste0("(d) ",westLab,",  w/o last b."))

fig2c <- draw_fig_4C(fig4C_EE_nl_plot_data,y_lims = c(0.01, 0.035)) + 
  labs(subtitle = paste0("(c) ",estLab,",  without last birth"))

### 2023-03-31 S2_draw_publication_plots.Rmd
group name adjustments

```{r}
library(ggplot2)
#some nice colors
bc <- c( "azure3","purple4", "navy", "darkgoldenrod2", "springgreen3", "black")

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  ggplot2::coord_cartesian() +
  labs(subtitle = "(a) Complete datasets",
       y="Per-birth twinning probability",
       x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data_nl,
              aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data_nl,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data_nl,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  labs(subtitle = "(b) Without last births",
       y="Per-birth twinning probability",
       x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

>>>>

```{r}
#some labels
estLab <- "Estonian"
westLab <- "9 other European"
```

```{r}
library(ggplot2)
#some nice colours
bc <- c( "azure3","purple4", "navy", "darkgoldenrod2", "springgreen3", "black")

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
            aes(y = estimate,  x=births_total, color=estLab),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  color=estLab, fill = estLab),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data,
            aes(y = estimate,  x=births_total, color=westLab),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill=westLab),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  ggplot2::coord_cartesian() +
  labs(subtitle = "(a) Complete datasets",
       y="Per-birth twinning probability",
       x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
             aes(y = estimate,  x=births_total, color=estLab),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data_nl,
              aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                  color=estLab, fill = estLab),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data_nl,
            aes(y = estimate,  x=births_total, color=westLab),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data_nl,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill=westLab),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  labs(subtitle = "(b) Without last births",
       y="Per-birth twinning probability",
       x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")
